---
title: "Covid91 vaccine study Final2020"
author: "Logan Kimbrough"
date: "11-20-2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)
#recode aids to say covid and then remove the annoying "X" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK" )) %>% select(-one_of("X"))
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine.

# Guys
```{r}
guysData <- filter(FinalData,sex=="guy")
``` 
```{r}
barchartGC(~infected + treatment,data=guysData)
barchartGC(~infected + treatment,data=guysData, type="percent")

```

Per the graph, the drug is not effective for the guys. It appears it is not helping the guys keeping from contracting covid. More people who took the drug got sick than those who took the placebo.

###  Numerical Summaries for guys 

```{r}
table1 <- xtabs(~infected + treatment, data=guysData)
rowPerc(table1)
colPerc(table1)
``` 

It appears that 58% of the people that got infected took the drug, and 42% got the placebo.

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Gals
```{r}
galsData <- filter(FinalData,sex=="gal")
```
```{r}
barchartGC(~infected + treatment,data=galsData)
barchartGC(~infected + treatment,data=galsData, type="percent")

```

It appears that the drug seems to be more effective for the gals. Fewer people got sick when taking the drug rather than taking the placebo. Approximately 64% of the people who took the drug got sick, where as approximately 36% of the people took the drug got sick.

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

# Drug Users
```{r}
DrugData <- filter(FinalData,DrugUser=="yes")
```
```{r}
barchartGC(~infected + treatment,data=DrugData)
barchartGC(~infected + treatment,data=DrugData, type="percent")

```

The Drug is working about the same for the drug users as it did for the gals. Approximately 64% of those who took the placebo got sick, and approximately 36% of those who took the drug got sick.

#  LGBTQ
```{r}
LGBTQData <- filter(FinalData,LGBTQ=="gay")
```
```{r}
barchartGC(~infected + treatment,data=LGBTQData)
barchartGC(~infected + treatment,data=LGBTQData, type="percent")

```

In this graph, it appears that the drug is not effective for the LGBTQ community. More than twice the number of people who took the drug than the placebo got sick with Covid.


###Numerical Summaries  

```{r}
table1 <- xtabs(~class + Sex, data=davisdata)
rowPerc(table1)
colPerc(table1)
```

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
